A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-11-05 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
making changes to match analytical

\begin{abstract}
    ABM is an effective tool for analysis of complex systems with long term 
    emergent behavior. In this study we apply ABM to analyse the long term 
    behavior of Keep’s random beacon. We look for the emergence of steady 
    state behavior, at which point we evaluate the sensitivity of specific 
    group and signature characteristics to various parameters. The results 
    of this study illustrates the effectiveness of ABM as an aid to the design 
    of novel distributed systems.

@@

\subsection{Compromised Groups}
We use the survival function of the hypergeometric distribution to determine
the likelihood of a group of n members being compromised. To do this we evaluate
the function at the max malicious threshold. (in the sim we have a separate compromised threshold)

>>>>

\begin{abstract}
    ABM is an effective tool for analysis of complex systems with long term 
    emergent behavior. In this study we apply ABM to analyse the long term 
    behavior of Keep’s random beacon. We look for the emergence of steady 
    state behavior, at which point we evaluate the sensitivity of specific 
    group and signature characteristics to various parameters. This study 
    illustrates the effectiveness of ABM as an aid to the design 
    of novel distributed systems. The team also intends to use this simulation
    as a way to analyze Keep system behavior after launch.

@@

\subsection{Compromised Groups}
We use the survival function of the hypergeometric distribution to determine
the likelihood of a group of n members being compromised. To do this we evaluate
the function at the max malicious threshold.
